### 2021-02-01 ch01_introduction/introduction.tex
Adapted key science questions

\section{Research Questions}
\label{sec:01:research_questions}

This section will present the \textbf{AWESOME} research questions!!!

\begin{enumerate}
  \item Did climate sensitivity change in the latest generation of \acp{ESM}
  from \acs{CMIP}6 and can we see progress compared to older climate model
  generations?

  \item Can we use emergent constraints established in \acs{CMIP}3 and
  \acs{CMIP}5 to reduce uncertainties in climate sensitivity in the \acs{CMIP}6
  ensemble?

  \item Can we use \ac{ML}-based approaches to constrain gridded projections of
  the future climate with observations?
\end{enumerate}

>>>>

\section{Key Science Questions}
\label{sec:01:research_questions}

This section will present the \textbf{AWESOME} key science questions!!!

\begin{enumerate}
  \item What is the range of climate sensitivity in the latest generation of
  \acp{ESM} compared to previous multi-model ensembles, and do we understand
  the processes that determine this uncertainty range?

  \item Can uncertainties in climate sensitivity be reduced with observations
  using the emergent constraint approach?

  \item Can uncertainties in multi-dimensional (gridded) climate projections be
  reduced with \ac{ML} techniques and observations?
\end{enumerate}
